DynaProg for Scala

### 2012-11-14 docs/roadmap/design.tex
Nits.

The algorithm proceeds as follows: first it solves the problem to obtain the first backtracking element, then it breaks the matrix in 4 submatrices, and refine it until backtrack is tractable. Since there is at most $\log n/b$ refinements and since every part of the matrix may be involved in backtrack, running time is $O(n^2 \log_2 n)$.
\item \textbf{Hybrid approach:} a hybrid approach might be created to take advantage of additional available memory, however, the running time decreases logarithmically to the space used.
\ule

>>>>

The algorithm proceeds as follows: first it solves the problem to obtain the first backtracking element, then it breaks the matrix in 4 submatrices, and refine it until backtrack is tractable. Since there is at most $\log n/b$ refinements and since every part of the matrix may be involved in backtrack, running time is $O(n^2 \log_2 n)$.
\item \textbf{Hybrid approach:} a hybrid approach might be created to take advantage of additional available memory, however, the running time decreases logarithmically to the space used, this means that using twice more storage space would only result in a $2\times$ speedup (measuring only the computation time). Hence an hybrid approach would be to decide a $k$ such that at each step we partition the desired submatix into a intermediate grid of $k$ rows/columns. The space usage would be in $2 k \log_k (n/b)$ and the running time complexity would be $O(n^2 \cdot \log_k n)$. Then the user would be able to fix a storage space $S \ge 4 \log_2 (n/b)$ and obtain the corresponding $k$ for a given $n$.
\ule

### 2012-11-14 docs/roadmap/draft.tex
More design.
Nits.

% ------------------------------------------------------------------------------------------------
\newpage
\section{Planning/draft}
\subsubsection*{Roadmap}
\begin{tabular}{rl}
16.11 & Rules normalization and automatic backtracking as in 5.2 \\
	& GenScala on LMS + GenCuda + LMS CudaCompiler \\
23.11 & Problem generalization: "cyclic keyword", Zucker problem / CudaLoop optimization \\
30.11 &--- Gap due to LMS missing knowledge \\
7.12 & Benchmarking, grammar analysis \\
14.12 & \\
21.12 & \\
28.12 & --- holiday --- \\
 4.01 & --- holiday --- \\
11.01 & Writing report: implementation description and plan for future work \\
18.01 & Writing report
\end{tabular}

>>>>

% ------------------------------------------------------------------------------------------------
\newpage
\section{Planning/draft}
\subsubsection*{Steps}\ul
\item Re-implement vanilla combinators with lists
\item Add following problems and features:\ul
	\item Polygon triangulation (cyclic problem)
	\item SWat with arbitrary gap (multi-track grammar)
	\item Zucker (rules of different complexity $O(n^2) / O(n)$)
	\item Rules normalization
	\item Rules dependency
	\item Automatic backtracking
	\ule
\item Test / proof that parsers are correct
\item Automate test to compare against implementation
\item Build bottom-up vanilla version\ul
	\item Separate initialization (terminals) and non-terminals (speed up?)
	\item In parallel implement the code generator for CUDA, hardcode in text function bodies for CUDA
	\ule
\item LMS implementation: from normal to Rep/Exp\ul
	\item Re-implement bottom-up vanilla into LMS
	\item Re-implement CUDA version and use functions body to infer CUDA code
	\ule
\item Write report
\item Further work\ul
	\item Serial for problems larger than memory, use hybrid (Myers and Miller's algorithm with $\log_k$ with $k$ depending on available memory) approach depending available memory
	\item 
	\ule
\ule

\subsubsection*{Roadmap}
\begin{tabular}{rl}
16.11 & Rules normalization and automatic backtracking as in 5.2 \\
	& GenScala on LMS + GenCuda + LMS CudaCompiler \\
23.11 & Problem generalization: "cyclic keyword", Zucker problem / CudaLoop optimization \\
30.11 &--- Gap due to LMS missing knowledge \\
7.12 & Benchmarking, grammar analysis \\
14.12 & \\
21.12 & \\
28.12 & --- holiday --- \\
 4.01 & --- holiday --- \\
11.01 & Writing report: implementation description and plan for future work \\
18.01 & Writing report
\end{tabular}
